Solar jet observed at the limb in SDO/SST

### 2016-05-24 paper/ms_temp_paper.tex
Begginning of the sst heat images

multi.placement = 't'
multi.caption = "a) Observe the two bright points in the proximity of $(79, 60)$. We the point on the left is significatly brighter than the feinter on the right. We emphasise that the brightening around $(60, 50)$ is not a contributor to this jet. b) In this frame the brightpoints have extended, the feinter point has now extended up to $~95$ and the core of the brighter left feature has grown with it. c) At this point the two seperate points are now indistinguishable and the feature is now extending as one column. "
\end{pycode}

@@

Essential in investigating jets is their effect on the atmosphere and what occurs at the boundary between jet and atmosphere.
As such, given that the jet is visible in most of the coronal lines we have created temperature maps of the jet and surrounding atmosphere using the method highlighted in \cite{Leonard2014}.

>>>>

multi.placement = 't!'
multi.caption = "a) Observe the two bright points in the proximity of $(79, 60)$. We the point on the left is significatly brighter than the feinter on the right. We emphasise that the brightening around $(60, 50)$ is not a contributor to this jet. b) In this frame the brightpoints have extended, the feinter point has now extended up to $~95$ and the core of the brighter left feature has grown with it. c) At this point the two seperate points are now indistinguishable and the feature is now extending as one column. "
\end{pycode}

@@

Essential in investigating jets is their effect on the atmosphere and what occurs at the boundary between jet and atmosphere.
With the high resolution of the CRISP instrument, we could possibly resolve some behaviour at the boundary between jet and atmosphere. 
To this end, we have visually inspected the jet, and what we find is demonstrated in % % %fig ref here

\begin{pycode}[SST_raw]
import numpy as np
from glob import glob
import sunpy.map
import matplotlib.pyplot as plt

im_1 = manager.data_file('core_Ha_dark_165.npy')
im_2 = manager.data_file('core_Ha_dark_170.npy')

afile = np.load(files[])
crop = afile[540:920, 420:610]
val_max = np.max(crop)
plt.imshow(crop, cmap='Greys_r', vmin=0.16*val_max, vmax=val_max, origin='lower', interpolation='none')

\end{pycode}

As such, given that the jet is visible in most of the coronal lines we have created temperature maps of the jet and surrounding atmosphere using the method highlighted in \cite{Leonard2014}.
